Hybrid platforms and bargaining power

### 2024-05-09 src/paper/application.tex
Finish rewriting intro

The rest of the paper is organized as follows.
In \cref{sec:model}, I introduce a general version of the model.
After that, \cref{sec:results}\footnote{
    \Cref{sec:more_general} explores the generalizability of these results, and highlights some common themes in settings with hybrid behavior.
} demonstrates results about bargaining outcomes one can derive even in this rather abstract setting.
\Cref{sec:example} concretizes the model by assuming a specific demand system, and also presents a corresponding benchmark model without bargaining.
\Cref{sec:extensions} then examines the effect of different assumptions about the bargaining process.
Finally, \cref{sec:conclusion} summarizes the results and discusses possible future work.

>>>>

The rest of the paper is organized as follows.
In \cref{sec:model}, I introduce two model of hybrid platforms: a benchmark with the platform setting an entry fee unilaterally, and the main model, where the platform and the fringe firms engage in bargaining.
After that, \cref{sec:results}\footnote{
    \Cref{sec:more_general} explores the generalizability of these results, and highlights some common themes in settings with hybrid behavior.
} demonstrates that the two have very different implications for consumer welfare.
\Cref{sec:extensions} then examines the effect of different assumptions about the bargaining process.
Finally, \cref{sec:conclusion} summarizes the results and discusses possible future work.
